\plaintitle

### 2015-11-08 Paper/paper.tex
Converted Evaluation into a Section
Added draft for Timeline

%TODO: Should be 1/2
\subsection{Evaluation}

@@

>>>>

%TODO: Should be 1/2
\section{Evaluation}

@@

\section{Timeline}
\begin{center}
    \begin{tabular}{ | l | p{5cm} |}
    \hline
      Date & Activity \\ \hline
      Day 0-7 & Planning of System Framework and Database Structures \\ \hline
      Day 8-14 & Implementation of Basic Backend Functions Without Conflict Checking \\ \hline
      Day 15-30 & Implementation of Conflict Checking and Integration with Backend \\ \hline
      Day 31-45 & Development of Static Web Application Interface \\ \hline
      Day 46-60 & Implementation of Advanced Features \\ \hline
      Day 61-68 & Stress Testing and Fuzzing \\ \hline
      Day 69-76 & Adjustments from the Results of Stress Testing and Fuzzing \\ \hline
      Day 77-81 & Alpha Test of Test Users \\ \hline
      Day 82-96 & Adjustments from the Results of Alpha Test \\ \hline
      Day 97-103 & Beta Release \\ \hline
    \end{tabular}
\end{center}
